\name: A hierarchical Bayesian model for Supernova Cosmology

### 2017-09-20 papers/methods/paper.tex
Paper updates

As such, staggering effort is being put into developing more sophisticated supernovae analyses. \citet{Scolnic2016} and \citet{Kessler2017} explore sophisticated simulation corrections to traditional analyses. Approximate Bayesian computation methods also make use of simulations, trading traditional likelihoods and analytic approximations for more robust models with only the cost of increased computational time \citep{Weyant2013, Jennings2016}. Hierarchical Bayesian Models abound \citep{Mandel2009, March2011, March2014a, Rubin2015, Shariff2016, Roberts2017}, however often face difficulties finding sufficient analytic approximations for complicated effects such as Malmquist bias.
\rule{\linewidth}{1pt}

@@

\section{Our Method}

@@

\section{Application to DES}

@@

\section{Systematics Strength Test}

@@

\section{Interesting Implementation Details}

Anything interesting.

>>>>

As such, staggering effort is being put into developing more sophisticated supernovae analyses. \citet{Scolnic2016} and \citet{Kessler2017} explore sophisticated simulation corrections to traditional analyses. Approximate Bayesian computation methods also make use of simulations, trading traditional likelihoods and analytic approximations for more robust models with only the cost of increased computational time \citep{Weyant2013, Jennings2016}. Hierarchical Bayesian Models abound \citep{Mandel2009, March2011, March2014a, Rubin2015, Shariff2016, Roberts2017}, however often face difficulties finding sufficient analytic approximations for complicated effects such as Malmquist bias.

In this paper, we lay out a new hierarchical model that extends on past work. In Section \ref{sec:method} we outline our methodology and apply it to simulated datasets. Forecasts for the impending DES three year spectroscopic supernova survey are contain in Section \ref{sec:des}. Section \ref{sec:sys} investigates the effect of various systematics on our model, and Section \ref{sec:details} provides details on potential areas of improvement and unsuccessful methodologies.

\rule{\linewidth}{1pt}

@@

\section{Our Method}
\label{sec:method}

@@

\section{Application to DES}
\label{sec:des}

@@

\section{Systematics Strength Test}
\label{sec:sys}

@@

\section{Interesting Implementation Details}
\label{sec:details}
Anything interesting.
